\chapter{Conclusion}

The group developed an application for HiØ MakerSpace.
The frontend was developed using Vue.js containing several pages such as a page for user registration, a page for user login and an index page displaying the items stored in the system.
The group also developed a backend using Node.js capable of fetching items as well as user registration, user authentication and user log out.
Additionally the backend allows the frontend to filter the items returned based on a category.
The group has had a focus on extendability as a software quality due to time restraints; the scope of the project does not permit the group to develop a fully flexed application.
As such the group opted to develop the core functionality the application would require; future development can thus proceed in whatever direction is deemed desirable by future developers of the application.

There are many features future developers could add to the application.
The application currently does not allow the user to search the repository of items nor does it allow the user to sort it based on a given condition.
The process of adding, updating or deleting items is currently a cumbersome process as it has to be done entirely through SQL statements; a more user friendly approach would be to develop a web page allowing administrators of the system to perform these processes using a UI.
The backend currently does not expose endpoints allowing administrators to add, update or delete items; as such endpoints would have to be developed to support the aforementioned UI.
Future developers could also opt to implement a loaning module allowing students and employees to borrow equipment; the group initially wanted to develop such a module during the very early stages of the project however the module was quickly dropped due to time and complexity constraints.

%The group has achieved several goals even though the group didn't achieve everything that was planned for the project.


%The group has managed to get a lot right with the project. With a frontend with a few essential functioning features and a strong backend. The groundwork is well done for finishing the remaining work easily, and the project even though not fully finished has achieved a lot.

